Draft Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-04-20 draftfinalreport_v3.tex
revisions for the final draft

\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-3 package
% Mon Apr 20 09:39:58 2015
\begin{tabular}{lrrrrrr}
  \hline
 & Df & Deviance & Resid. Df & Resid. Dev & F & Pr($>$F) \\ 
  \hline
NULL &  &  & 59 & 1532.80 &  &  \\ 
  Age & 4 & 1345.17 & 55 & 187.63 & 204.01 & 0.0000 \\ 
  Ethnicity & 3 & 19.88 & 52 & 167.75 & 4.02 & 0.0141 \\ 
  NZDep & 2 & 17.10 & 50 & 150.65 & 5.19 & 0.0102 \\ 
  Age:Ethnicity & 12 & 80.80 & 38 & 69.85 & 4.09 & 0.0004 \\ 
   \hline
\end{tabular}\caption{Significance of different predictor variables for measles risk factors from 2007-2014, estimated using \autoref{eq:reg} and a quasipoisson error structure}
\label{table:anova}
\end{table}

\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-3 package
% Mon Apr 20 09:39:58 2015
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & -6.1644 & 0.1267 & -48.65 & 0.0000 \\ 
  Age2-4 & -1.0351 & 0.1972 & -5.25 & 0.0000 \\ 
  Age5-17 & -0.9954 & 0.1368 & -7.28 & 0.0000 \\ 
  Age18-24 & -1.7204 & 0.1926 & -8.93 & 0.0000 \\ 
  Age25+ & -3.1697 & 0.1622 & -19.55 & 0.0000 \\ 
  EthnicityAsian & 0.2464 & 0.3168 & 0.78 & 0.4415 \\ 
  EthnicityMaori & 0.2081 & 0.2121 & 0.98 & 0.3327 \\ 
  EthnicityPacific & 1.2200 & 0.2134 & 5.72 & 0.0000 \\ 
  NZDep4-7 & -0.2609 & 0.0948 & -2.75 & 0.0090 \\ 
  NZDep8-10 & -0.3043 & 0.1040 & -2.93 & 0.0058 \\ 
  Age2-4:EthnicityAsian & -2.3148 & 1.3319 & -1.74 & 0.0903 \\ 
  Age5-17:EthnicityAsian & -1.2453 & 0.4566 & -2.73 & 0.0096 \\ 
  Age18-24:EthnicityAsian & -1.0187 & 0.5743 & -1.77 & 0.0841 \\ 
  Age25+:EthnicityAsian & 0.2344 & 0.4298 & 0.55 & 0.5887 \\ 
  Age2-4:EthnicityMaori & -0.1013 & 0.3644 & -0.28 & 0.7826 \\ 
  Age5-17:EthnicityMaori & -0.1032 & 0.2521 & -0.41 & 0.6846 \\ 
  Age18-24:EthnicityMaori & -0.5723 & 0.4409 & -1.30 & 0.2022 \\ 
  Age25+:EthnicityMaori & -1.0349 & 0.5127 & -2.02 & 0.0506 \\ 
  Age2-4:EthnicityPacific & -0.9798 & 0.4676 & -2.10 & 0.0429 \\ 
  Age5-17:EthnicityPacific & -1.5709 & 0.3312 & -4.74 & 0.0000 \\ 
  Age18-24:EthnicityPacific & -1.0354 & 0.5003 & -2.07 & 0.0453 \\ 
  Age25+:EthnicityPacific & -0.6629 & 0.4279 & -1.55 & 0.1296 \\ 
   \hline
\end{tabular}\caption{Summary of the regression model results using \autoref{eq:reg} and a quasipoisson error structure, for measles risk factors for cases from 2007-June 2014}
\label{table:regression_riskfactors}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12006[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.9231$&$0.9604$&$0.9457$&$1$&$1$&$318$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR1 across the 2013 area units. See \autoref{fig:fig12006}.}
\label{table:tab12006}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22006[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.8611$&$0.9167$&$0.9029$&$0.9714$&$1.143$&$318$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR2 across the 2013 area units. See \autoref{fig:fig22006}.}
\label{table:tab22006}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12007[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.9286$&$0.9621$&$0.9499$&$1$&$1$&$324$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2007 birth cohort vaccinated against MMR1 across the 2013 area units. See \autoref{fig:fig12007}.}
\label{table:tab12007}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22007[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.8592$&$0.9099$&$0.899$&$0.9643$&$1$&$324$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2007 birth cohort vaccinated against MMR2 across the 2013 area units. See \autoref{fig:fig22007}.}
\label{table:tab22007}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12008[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.9365$&$0.971$&$0.9569$&$1$&$1$&$315$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2008 birth cohort vaccinated against MMR1 across the 2013 area units. See \autoref{fig:fig12008}.}
\label{table:tab12008}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22008[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.8451$&$0.9048$&$0.8908$&$0.9583$&$1$&$315$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2008 birth cohort vaccinated against MMR2 across the 2013 area units. See \autoref{fig:fig22008}.}
\label{table:tab22008}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12009[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.939$&$0.9722$&$0.9575$&$1$&$1$&$324$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2009 birth cohort vaccinated against MMR1 across the 2013 area units. See \autoref{fig:fig12009}.}
\label{table:tab12009}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22009[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.8302$&$0.8889$&$0.8773$&$0.9444$&$1$&$324$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2009 birth cohort vaccinated against MMR2 across the 2013 area units. See \autoref{fig:fig22009}.}
\label{table:tab22009}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12010[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0.0714$&$0.9326$&$0.9667$&$0.9557$&$1$&$1$&$321$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2010 birth cohort vaccinated against MMR1 across the 2013 area units. See \autoref{fig:fig12010}.}
\label{table:tab12010}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22010[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.625$&$0.7059$&$0.6974$&$0.7791$&$1$&$321$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2010 birth cohort vaccinated against MMR2 across the 2013 area units. See \autoref{fig:fig22010}.}
\label{table:tab22010}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12011[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.9286$&$0.9643$&$0.9492$&$1$&$1$&$326$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2011 birth cohort vaccinated against MMR1 across the 2013 area units. See \autoref{fig:fig12011}.}
\label{table:tab12011}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22011[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0$&$0.0345$&$0.0606$&$0.0893$&$1$&$326$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2011 birth cohort vaccinated against MMR2 across the 2013 area units. See \autoref{fig:fig22011}.}
\label{table:tab22011}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12012[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.9333$&$0.9667$&$0.9527$&$1$&$1$&$331$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2012 birth cohort vaccinated against MMR1 across the 2013 area units. See \autoref{fig:fig12012}.}
\label{table:tab12012}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22012[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0$&$0.0041$&$0.0403$&$0.0476$&$1$&$331$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2012 birth cohort vaccinated against MMR2 across the 2013 area units. See \autoref{fig:fig22012}.}
\label{table:tab22012}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12013[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.5556$&$0.6333$&$0.6276$&$0.7$&$1$&$331$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR1 across the 2013 area units. See \autoref{fig:fig12013}.}
\label{table:tab12013}
\end{table}

@@

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v3-032}
\end{center}
\caption{Trend in global per capita measles incidence}
\label{fig:trendincidence}
\end{figure}

@@

Data to estimate the costs relating to the current measles outbreak were obtained from the New Zealand Ministry of Health, for the period 2008 through June 2014. Data include information on gender of the case, ethnicity and age of the case at discharge from hospital, days spent in the hospital, year of case, number of events, and associated cost.

>>>>

\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-3 package
% Mon Apr 20 18:11:35 2015
\begin{tabular}{lrrrrrr}
  \hline
 & Df & Deviance & Resid. Df & Resid. Dev & F & Pr($>$F) \\ 
  \hline
NULL &  &  & 59 & 1532.80 &  &  \\ 
  Age & 4 & 1345.17 & 55 & 187.63 & 204.01 & 0.0000 \\ 
  Ethnicity & 3 & 19.88 & 52 & 167.75 & 4.02 & 0.0141 \\ 
  NZDep & 2 & 17.10 & 50 & 150.65 & 5.19 & 0.0102 \\ 
  Age:Ethnicity & 12 & 80.80 & 38 & 69.85 & 4.09 & 0.0004 \\ 
   \hline
\end{tabular}\caption{Significance of different predictor variables for measles risk factors from 2007-2014, estimated using \autoref{eq:reg} and a quasipoisson error structure}
\label{table:anova}
\end{table}

\vspace{5mm} %5mm vertical space
\begin{table}
% latex table generated in R 3.0.2 by xtable 1.7-3 package
% Mon Apr 20 18:11:35 2015
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & -6.1644 & 0.1267 & -48.65 & 0.0000 \\ 
  Age2-4 & -1.0351 & 0.1972 & -5.25 & 0.0000 \\ 
  Age5-17 & -0.9954 & 0.1368 & -7.28 & 0.0000 \\ 
  Age18-24 & -1.7204 & 0.1926 & -8.93 & 0.0000 \\ 
  Age25+ & -3.1697 & 0.1622 & -19.55 & 0.0000 \\ 
  EthnicityAsian & 0.2464 & 0.3168 & 0.78 & 0.4415 \\ 
  EthnicityMaori & 0.2081 & 0.2121 & 0.98 & 0.3327 \\ 
  EthnicityPacific & 1.2200 & 0.2134 & 5.72 & 0.0000 \\ 
  NZDep4-7 & -0.2609 & 0.0948 & -2.75 & 0.0090 \\ 
  NZDep8-10 & -0.3043 & 0.1040 & -2.93 & 0.0058 \\ 
  Age2-4:EthnicityAsian & -2.3148 & 1.3319 & -1.74 & 0.0903 \\ 
  Age5-17:EthnicityAsian & -1.2453 & 0.4566 & -2.73 & 0.0096 \\ 
  Age18-24:EthnicityAsian & -1.0187 & 0.5743 & -1.77 & 0.0841 \\ 
  Age25+:EthnicityAsian & 0.2344 & 0.4298 & 0.55 & 0.5887 \\ 
  Age2-4:EthnicityMaori & -0.1013 & 0.3644 & -0.28 & 0.7826 \\ 
  Age5-17:EthnicityMaori & -0.1032 & 0.2521 & -0.41 & 0.6846 \\ 
  Age18-24:EthnicityMaori & -0.5723 & 0.4409 & -1.30 & 0.2022 \\ 
  Age25+:EthnicityMaori & -1.0349 & 0.5127 & -2.02 & 0.0506 \\ 
  Age2-4:EthnicityPacific & -0.9798 & 0.4676 & -2.10 & 0.0429 \\ 
  Age5-17:EthnicityPacific & -1.5709 & 0.3312 & -4.74 & 0.0000 \\ 
  Age18-24:EthnicityPacific & -1.0354 & 0.5003 & -2.07 & 0.0453 \\ 
  Age25+:EthnicityPacific & -0.6629 & 0.4279 & -1.55 & 0.1296 \\ 
   \hline
\end{tabular}\caption{Summary of the regression model results using \autoref{eq:reg} and a quasipoisson error structure, for measles risk factors for cases from 2007-12 June 2014}
\label{table:regression_riskfactors}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12006[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.9231$&$0.9604$&$0.9457$&$1$&$1$&$318$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12006}.}
\label{table:tab12006}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22006[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.8611$&$0.9167$&$0.9029$&$0.9714$&$1.143$&$318$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22006}.}
\label{table:tab22006}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12007[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.9286$&$0.9621$&$0.9499$&$1$&$1$&$324$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2007 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12007}.}
\label{table:tab12007}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22007[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.8592$&$0.9099$&$0.899$&$0.9643$&$1$&$324$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2007 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22007}.}
\label{table:tab22007}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12008[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.9365$&$0.971$&$0.9569$&$1$&$1$&$315$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2008 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12008}.}
\label{table:tab12008}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22008[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.8451$&$0.9048$&$0.8908$&$0.9583$&$1$&$315$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2008 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22008}.}
\label{table:tab22008}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12009[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.939$&$0.9722$&$0.9575$&$1$&$1$&$324$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2009 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12009}.}
\label{table:tab12009}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22009[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.8302$&$0.8889$&$0.8773$&$0.9444$&$1$&$324$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2009 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22009}.}
\label{table:tab22009}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12010[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0.0714$&$0.9326$&$0.9667$&$0.9557$&$1$&$1$&$321$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2010 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12010}.}
\label{table:tab12010}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22010[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.625$&$0.7059$&$0.6974$&$0.7791$&$1$&$321$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2010 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22010}.}
\label{table:tab22010}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12011[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.9286$&$0.9643$&$0.9492$&$1$&$1$&$326$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2011 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12011}.}
\label{table:tab12011}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22011[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0$&$0.0345$&$0.0606$&$0.0893$&$1$&$326$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2011 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22011}.}
\label{table:tab22011}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12012[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.9333$&$0.9667$&$0.9527$&$1$&$1$&$331$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2012 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12012}.}
\label{table:tab12012}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t22012[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0$&$0.0041$&$0.0403$&$0.0476$&$1$&$331$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2012 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22012}.}
\label{table:tab22012}
\end{table}

@@

 \vspace{5mm} %5mm vertical space
\begin{table}
%latex.default(t12013[1:7], file = "", table.env = FALSE, rowname = NULL)%
\begin{center}
\begin{tabular}{rrrrrrr}
\hline\hline
\multicolumn{1}{c}{Min}&\multicolumn{1}{c}{1st Q}&\multicolumn{1}{c}{Median}&\multicolumn{1}{c}{Mean}&\multicolumn{1}{c}{3rd Q}&\multicolumn{1}{c}{Max}&\multicolumn{1}{c}{NA}\tabularnewline
\hline
$0$&$0.5556$&$0.6333$&$0.6276$&$0.7$&$1$&$331$\tabularnewline
\hline
\end{tabular}\end{center}\caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12013}.}
\label{table:tab12013}
\end{table}

@@

\begin{figure}
\begin{center}
\includegraphics{draftfinalreport_v3-034}
\end{center}
\caption{Trend in global per capita measles incidence}
\label{fig:trendincidence}
\end{figure}

@@

Data to estimate the costs relating to the current measles outbreak were obtained from the New Zealand Ministry of Health, for the period 2008 through 12 June 2014. Data include information on gender of the case, ethnicity and age of the case at discharge from hospital, days spent in the hospital, year of case, number of events, and associated cost.
